\input{settings.tex}
\input{macros}

\title{Intersection of Unions Flowpipe for Minimizing Multi-Directional Linearization Error}
\titlerunning{Intersection of Unions Flowpipe for Minimizing Multi-Directional}
\author{}
\institute{}
%
\begin{document}    
\maketitle
%
\begin{abstract}
We propose a new efficient method for computing an overapproximation
of a set of trajectories, called \emph{flowpipe}, for a system
described by uncertain nonlinear differential equations.  Since
reachable sets of linear systems can be computed efficiently,
piecewise linearization of nonlinear ODEs is a commonly used technique
while computing flowpipes.  However, the number of pieces required in
piecewise linearization becomes exponential in the dimension for
minimizing the linearization error below any threshold value, which
can be computationally intractable in high dimensions.  Alternatively,
if the number of divisions is fixed, we need to optimize the way the
reach set is divided to minimize the linearization error.  Since the
linearization error is multi-dimensional, this minimization is a
multi-objective optimization problem that does not have a single best
solution.  However, a previous method in literature proposed to
minimize a single dimensional measure while dividing the reachable
sets, which does not necessarily reduce the linearization error along
all coordinates.  In this paper, we propose a better method where we
use multiple best optimal ways of division, instead of a single way of
division, for minimizing linearization error along multiple
directions.  Consequently, we represent the resulting reachable sets
as the intersection of unions (IoU), where each intersecting union
corresponds to the optimized division for each direction among
multiple directions.  We propose an algorithm to propagate the
resulting IoU of sets such that the linearization error is reduced
significantly along every direction in a set of multiple directions.
As a proof of concept, we evaluate our algorithm on an illustrative
example and two high dimensional real-world examples and demonstrate a
high increase in the flowpipe accuracy compared to the earlier method
of division and other state-of-the-art methods.
\is{abstract may be a bit shorter.}
\end{abstract}

\section{Introduction}
\input{sections/intro}
%
\section{Preliminaries}
\input{sections/notation}
%\subsection{Nonlinear system and linearization}
%\input{sections/system}~\label{sec:system}
%
\section{Problem}
\input{sections/problem}
%
\section{Solution}
\input{sections/newmethod}
%
\section{Evaluation}~\label{sec:eval}
\input{sections/evaluation}
%
\section{Conclusion}
\input{sections/conclusion}






\bibliographystyle{plain}
\bibliography{ref}

\newpage
\section{Appendix}
\input{sections/appendix}


\end{document}
