Dividing reachable set to restrict the linearization error below a
threshold can become computationally intractable in high dimensional
spaces.  Alternatively, we can fix the number of pieces and then find
a good division of the reach set that minimizes the linearization
error.  However, the linearization error being multi-dimensional, the
required optimization is multi-objective which has no single best
solution.  We addressed this issue by using intersection of unions,
where each intersecting union corresponds to an optimized division for
one direction of linearization error.  Evaluation of this method on
real world examples showed high increase in accuracy compared to
state-of-the-art techniques and an earlier method of division that uses only unions instead of intersection of unions.

There is a large scope for improvement of our method.  The
intersection between interval zonotopes is not computed very
accurately in this algorithm.  If this is improved, we can get
further gain in accuracy.  Furthermore, we only divide the
reachable set in the initial time interval because iterative division
increases the number of pieces and the complexity of representing the
reachable sets.  Thus, we need to find a way of controlling the
complexity of set representation while making iterative division such
that the resulting abstraction error is small.  Furthermore, we
believe that a GPU implementation of our parallel algorithm,
instead of using multiple CPUs, will result in better scalability.
