We consider an $n$-dimensional nonlinear system with $m$-inputs
$H=\rb{f,U,\reals^n}$.  A flowpipe of $H$ in a time interval $[0,T)$
from an initial set $\init\in\intervals^n$ is a mapping
$\trfn{X}:[0,T]\rightarrow \set{\Omega\st{\Omega\subseteq \reals^n}}$
such that $\forall t\in[0,T]~\reach{H}{t}{Q}\subseteq \tr{X}{t}$. 
\is{What is $Q$ here?}
We
will first discuss the motivation for using an intersection of union sets
for representing flowpipes.
%
\subsection{Motivation for intersection of unions}
In the previous section, we showed how to compute an overapproximation
of the reachable set at time $t$ starting from an interval zonotope
$\zt = \rb{\gen,\cen,\bounds}$.
%% Using that, we can compute a flowpipe inductively as follows.  We
%% divide $[0,T]$ into small time intervals
%% $\rb{[0,\delta],[\delta,2\delta],\ldots,[N\delta,T]}$.  Then,
%% %
%% \begin{enumerate}
%% \item $\tr{X}{0} = \ztset{\rb{\diag{\sup\rb{\rad{X_o}}},\mi{X_0},X_0}}$,
%% i.e. convert initial set to an interval zonotope representation.
%% \item $\forall i\in\integers_{\geq 0}\tr{X}{(i+1)\delta} = \ztset{\flow{H}{t}{K}{\epsilon}{\tr{X}{i\delta}}}$.
%% \item $\forall t\in[i\delta,(i+1)\delta]\tr{X}{t} = {\ivflow{H}{t}{K}{\epsilon}{\tr{X}{i\delta}}}$.
%% \end{enumerate}
%% %
However, the above method incurs a Taylor error
$\taylor{f}{\ivflow{H}{t}{K}{\epsilon}{\ztset{\zt}}}{U}$.  The Taylor
error is positively correlated to the the width
$\sup\rb{\rad{\bounds}}$ of the interval bounds of the interval
zonotope~(see Equations~\ref{eqn:linearize}).  So, we can reduce the
linearization error by dividing the interval zonotope into smaller
sets and computing the next reachable set as union of reachable sets
of constituting pieces.  But dividing a set into sets of a given
fixed size results in exponential number of divisions in the dimension
of the state space, which can be computationally prohibitive.
Instead, we can divide the reach set into a fixed number of subsets.
For a fixed number of divisions $2^\eta\in\integers$, there are many
ways of dividing the reachable set.  Then, we have to find a division
that minimizes the Taylor error.  In this context, a performance index
was proposed by bAlthoff et.al.~\cite{althoff2008reachability} to
divide reachable sets as follows.  A reachable set $\Omega$ is divided
into two sets $\Omega_1$ and $\Omega_2$ which minimizes the following
quantity for a user chosen threshold $\rho\in\reals^n_{>0}$:
%
\begin{align*}
\sup_{i=1}^n\frac{{\sup{\taylor{f}{\Omega_1}{U}}}_i}{\rho_i}\sup_{i=1}^n\frac{\sup{\taylor{f}{\Omega_2}{U}}_i}{\rho_i}.~\numberthis\label{eqn:pi}
\end{align*}
%
\paragraph{Drawback:}  Since the linearization error is
multi-dimensional, minimizing it is a multi-objective optimization
problem which does not have a single best solution.  But the above
performance index is a one dimensional measure of the overall
linearization error.  Minimizing this one dimensional performance
index does not necessarily reduce signifcantly the linearization error
along all coordinates.  For illustration, let us consider the
nonlinear system in Example~\ref{eg:ill}.  Let $\Omega =
[-1,1]\times[-0.5,0.5]\times[-0.1,0.1]$ be the reachable set at a time
point and we take the linearization error before splitting $\rho
= \taylor{f}{\Omega}{U}$ as the threshold for splitting.  Using the
above performance index, we get that $\Omega$ should be split along
$x$-axis into $\Omega_1 = [-1,0]\times[-0.5,0.5]\times[-0.1,0.1]$ and
$\Omega_2 = [0,1]\times[-0.5,0.5]\times[-0.1,0.1]$.  However, there
will be very little reduction in the linearization error along
$y$-axis, which least depends on the width along $x$-axis due to the
multiplication coefficient $0.1$ of $xy$ in $f_3$.  Instead, the best
division to minimize the $y$-directional linearization error is to
divide along $y$-coordinate as $\Omega =
[-1,1]\times[-0.5,0]\times[-0.1,0.1]$ and $\Omega_2 =
[-1,1]\times[0,0.5]\times[-0.1,0.1]$.  This means reducing the
linearization error using the above performance index need not
significantly reduce the linearization error along all coordinates.
Besides, it is not known how to choose a threshold $\rho$ for good
flowpipe accuracy.

\paragraph{New method:}  In this paper, we propose an better approach
that ensures reduction in the linearization error that along each
individual direction in a finite set of directions. 
\is{An extra ``that'' in the previous sentence.}
To do so, we
use \emph{intersection of unions} (IoU).  For each direction, we find
an optimized division of the reach set for reducing the linearization
error.  Then we intersect the union sets corresponding to the
optimized division for linearization error along each direction.  This
way, we ensure that the linearization error is significantly reduced
along each direction in the given set of directions.

As a heuristic, we choose the directions as the eigenvectors of the
nonlinear system at the origin.  Furthermore, we only divide the initial set
because of two reasons.
%
\begin{enumerate}
\item Dividing a reach set increases the representation complexity due to
increase in the number of elements in the union.  So, iterative
division of reach set at various time stamps will blow up the
representation complexity.
\item  An interval zonotope which is not an interval can not
be divided accurately and reduces the accuracy of flowpipe.
\end{enumerate}
%
Henceforth, we only divide the initial set, which is an interval, to
compute an intersection of unions representation.
%
\subsection{Computing set of optimized division vectors:}
Let us denote $\bounds=X_0$ \is {What is $X_0$?}.  Given a vector of positive integer
values $q\in\integers_{>0}$, called \emph{division vector} \is{$q$ is a scalar here}, we define
a union of interval vectors which is a close overapproximation of $h$
with only floating point approximation error, as follows.  The set of
the set of divided interval vectors corresponding to division vector
$q$ is
%
\begin{align*}
D_q
= & \left\{r_1\times...\times r_n\right.\\
& \left.\st{\forall i\in\set{1,\ldots,n}~r_i
= \ivmat{\inf\rb{\bounds_i}}+k_i\frac{\rad{\bounds}_i}{q_i}, k_i\in\set{1,\ldots,q_i}}\right\}.
\end{align*}
\is{The value of $k_i$ is  not clear in the  above equation.}
%
For all intervals in $D_q$, an upper bound on the Taylor error is
given below.
%
\begin{align*}
\rb{\utaylor{f}{U}{\bounds}{q}}_i
= \frac{1}{2}\sum_{k=1}^{n}\sum_{j=1}^{n}\rb{\nabla_k\nabla_j{f_i}\rb{\bounds}}\frac{\rad{\bounds_k}}{q_k}\frac{\rad{\bounds_j}}{q_j}
\\
+ \frac{1}{2}\sum_{k=n+1}^{n+m}\sum_{j=n+1}^{n+m}\rb{\nabla_k\nabla_j{f_i}\rb{\bounds}}\rad{U_k}\rad{U_j}
\end{align*}
%
For any $k\in\set{1,\ldots,n}$, the projection of the upper bound
along the $k^{th}$ eigenvector is given by
$\utaylor{f}{U}{\bounds}{q}\eig_{:,k}
= \utaylor{f}{U}{\bounds}{q}\real{\eig_{:,k}}
+ \iota\utaylor{f}{U}{\bounds}{q}\imag{\eig_{:,i}}$.  We select $q$ to
reduce the maximum absolute value of this bound, by using the
following greedy optimization.  Let us consider for any
$i\in\set{1,\ldots,n}$, $\omega\rb{q,i}\in\integers^n$ where $\omega\rb{q,i}_j
= \begin{cases}2q_j & j=i\\ q_j & i\neq j \end{cases}$.

\begin{algorithm}
\caption{Optimizing division vector for $k^{th}$
eigenvector} $q\gets \mymatrix{1,\ldots,1}^T\in\integers^n$\;
\While{$\prod_{j=1}^nq_j<2^\eta$}{
$ind \gets \argmin_{i=1}^n\begin{cases}\rb{\sup\rb{\real{\utaylor{f}{U}{\bounds}{\omega\rb{q,i}}\eig_{:,k}}}}^2\\
 + \rb{\sup\rb{\imag{\utaylor{f}{U}{\bounds}{\omega\rb{q,i}}\eig_{:,k}}}}^2\end{cases}$\;
$q\gets \omega\rb{q,ind}$
}
\end{algorithm}
%
We denote the set of optimized division vectors correponding to
minimizing the projection of Taylor error along different eigenvectors
as $\dopt{\eta}$, where $2^\eta$ is the maximum number of divisions.
%
\begin{example}
Let us consider the nonlinear system $H$ in Example~\ref{eg:ill}, an
interval vector $h = [0,1]^3$ and maximum number of divisions $\eta =
4$.  The eigenvectors at the origin are the coordinate vectors
$\mymatrix{1 & 0 & 0}^T$, $\mymatrix{0 & 1 & 0}^T$ and $\mymatrix{0 &
0 & 1}^T$.  To reduce the linearization error along $\mymatrix{1 & 0 &
0}^T$, the best possible division vector is $\mymatrix{2 & 1 & 2}^T$,
i.e., divide $x$ and $\theta$ coordinates.  For the direction
$\mymatrix{0 & 1 &0}^T$, the optimum division vector is $\mymatrix{1 &
2 & 2}^T$ and for the direction $\mymatrix{0 & 0 & 1}^T$, the optimum
division vector is $\mymatrix{1 & 1 & 4}^T$.  So, $\dopt{4}
= \set{\mymatrix{2 & 1 & 2}^T, \mymatrix{1 & 2 & 2}^T, \mymatrix{1 & 1
& 4}^T}$.  The three different division vectors results three
different kinds of divisions of $[0,1]^3$ whose intersection is
represented as an IoU of interval zonotopes.
\end{example}
%
\subsection{Casting initial set as intersection of unions}
For a division vector $q\in\dopt{\eta}$, we can closely
overapproximate $X_0$ as a union of interval zonotopes of order $l>0$
as $\bigcup_{b\in D_q}\lin{\zerozon{n}{l}}{\sqb{0}_{n\times n}}{b}$
with only floating point overapproximation error.  To reduce the
Taylor error along each eigenvector, we store the union corresponding
to each optimized division vector in $\dopt{\eta}$ and take their
intersection.  The resulting intersection of unions is
%
\begin{align*}
\bigcap_{q\in\dopt{\eta}}\bigcup_{b\in
D_q}\lin{\zerozon{n}{l}}{\sqb{0}_{n\times n}}{b}~\numberthis\label{eqn:iouopt}
\end{align*}
%
In a computer, we represent an intersection of unions of interval zonotope sets as above with a matrix of interval zonotope tuples, called \emph{IoU interval zonotope}.
%
\begin{definition}[IoU interval zonotope]
An IoU zonotope $\zt$ is a matrix of interval zonotopes which
represents the set
%
\[
\ztset{\zt} = \bigcap_{i=1}^{\rows{\zt}}\bigcup_{i=1}^{\cols{\zt}}\ztset{\zt_{ij}}.
\]
%
\end{definition}
%
We represent the optimized intersection of unions in
Equation~\ref{eqn:iouopt} by an IoU interval zonotope, which we denote by
$\iouopt{\eta}{X_0}$ which is assigned as follows.
%
\begin{algorithm}\caption{Initial IoU zonotope assignment}
$i\gets 1$,~$j\gets 1$\;
\For{$q\in\dopt{q}$}{
\For{$b\in D_q$}{
$\rb{\iouopt{\eta}{X_0}}_{ij} \gets \lin{\zerozon{n}{l}}{\sqb{0}_{n\times n}}{b}$\;
$j\gets j+1$\; } $i\gets i+1$\; }
\end{algorithm}
%
\subsection{Computing IoU flowpipe}
For an IoU interval zonotope, we can compute the reachable
set at time $t$ according to the following lemma.
%
\begin{lemma}~\label{lem:ioureach}
Let us consider an IoU of interval zonotopes $\zt$,
$K\in\integers_{\geq 0}$, $\epsilon\in\reals_{>0}$.  Let us consider
IoU interval zonotopes $\flow{H}{t}{K}{\epsilon}{\zt}$ and
$\ivflow{H}{t}{K}{\epsilon}{\zt}$ defined as
%
\begin{align*}
\rb{\flow{H}{t}{K}{\epsilon}{\zt}}_{ij}
= \flow{H}{t}{K}{\epsilon}{\zt_{ij}},~~~
\rb{\ivflow{H}{t}{K}{\epsilon}{\zt}}_{ij}
= \ivflow{H}{t}{K}{\epsilon}{\zt_{ij}}.
\end{align*}
%
Then
$\reach{H}{t}{\zt}\subseteq \ztset{\flow{H}{t}{K}{\epsilon}{\zt}}$ and
$\reach{H}{[0,t]}{\zt}\subseteq \ivflow{H}{t}{K}{\epsilon}{\zt}$.
\end{lemma}
%
\begin{proof}
Let us consider a trajectory $\trfn{x}$ such that $\tr{x}{0}\in\ztset{\zt}$.
This means $\forall i\in\set{1,\ldots,N} \exists
j_i:\tr{x}{0}\in\ztset{\zt_{ij_i}}$.  By Lemma~\ref{lem:reachnonlin}, we get
that $\forall
i\in\set{1,\ldots,N}~\tr{x}{t}\in\ztset{\flow{H}{t}{K}{\epsilon}{\ztset{\zt_{ij_i}}}}$
and by Lemma~\ref{lem:bloat} we get that $\forall t\in[0,t]\forall
i\in\set{1,\ldots,N}~\tr{x}{t}\in\ivflow{H}{t}{K}{\epsilon}{\ztset{\zt_{ij_i}}}$.
This proves the lemma.
\end{proof}
%
For an IoU interval zonotope, we can refine the interval bounds in
each of its constituting elements as follows. 
%
\begin{lemma}~\label{lem:refine}
Let $\zt$ be an IoU interval zonotope where $\zt_{ij}
= \rb{\gen^{ij},\cen^{ij},\bounds^{ij}}$.  Let us consider $\widehat{\bounds}
= \bigwedge_{i=1}^{\rows{\zt}}\bigvee_{j=1}^{\cols{\zt}}\bounds^{ij}$.  We
define a refined IoU interval zonotope $\refine\rb{\zt}$ as
%
\[
\rb{\refine\rb{\zt}}_{ij}
= \rb{\gen^{ij},{\cen^{ij}},{\meet{\bounds^{ij}}
{\widehat{\bounds}}}}.
\]
%
Then $\ztset{\zt} = \ztset{\refine\rb{\zt}}$.
\end{lemma}
%
The above lemma is straighforward to derive.  In this refined
representation, we reduce the interval bounds in each constitution
element of the IoU based on the overall interval bounds $\widehat{\bounds}$
given above.

Now we have the results to compute an optimized IoU zonotope flowpipe.
The flowpipe computation is described in Algorithm~\ref{alg:main}.
The correctness of the algorithm is proved in Theorem~\ref{thm:main}.
%
\begin{algorithm}\caption{IoU interval zonotope
flowpipe computation}\label{alg:main}
\KwData{$n$-dimensional system with $m$ inputs $H = \rb{f,U,\reals^n}$,
$T\in\reals_{\geq 0}$, $X_0\in\intervals^n$.}

\KwResult{Flowpipe $\trfn{X}:[0,T]\rightarrow \set{\text{Set of IoU interval
zonotopes and intervals}}|~\tr{X}{0}\supseteq X_0$.}

Choose $\eta,K\in\integers$, $\epsilon,\delta\in\double_{>0}$.

$\tr{X}{0}\gets \iouopt{\eta}{X_0}$.

$i\gets 0.$

\While{$i\delta\leq N$}{
$\tr{X}{(i+1)\delta} = \refine\rb{\flow{H}{\delta}{K}{\epsilon}{\tr{X}{i\delta}}}$.~\label{step:1}

$\forall t\in(i\delta,(i+1)\delta) \tr{X}{t} = \ivflow{H}{\delta}{K}{\epsilon}{\tr{X}{i\delta}}$.~\label{step:2}

$i \gets i+1$.
}
\end{algorithm}
%
\begin{theorem}~\label{thm:main}
Let us consider the candidate flowpipe $\trfn{X}$ computed in
Algorithm~\ref{alg:main}.  For all $t\in[0,T]$,
$\reach{H}{t}{X_0}\subseteq \ztset{\tr{X}{t}}$.
\end{theorem}
%
\begin{proof}
We prove the theorem inductively.

\paragraph{Claim:}  Let us consider that for some
$i\in\integers_{\geq 0}:i\delta<T$, we have
$\reach{H}{i\delta}{X_0}\subseteq\tr{X}{i\delta}$.  Then $\forall
t\in[i\delta,(i+1)\delta]~\reach{H}{t}{X_0}\subseteq \ztset{\tr{X}{t}}$.

\paragraph{Proof of claim:}
By Lemmas~\ref{lem:ioureach} and~\ref{lem:refine}, we get
$\reach{H}{\delta}{\tr{X}{i\delta}}\subseteq \ztset{\flow{H}{\delta}{K}{\epsilon}{\tr{X}{i\delta}}}$
and\\
$\reach{H}{[0,\delta]}{\tr{X}{i\delta}}\subseteq \ivflow{H}{\delta}{K}{\epsilon}{\tr{X}{i\delta}}$.
But we assumed $\reach{H}{i\delta}{X_0}\subseteq \tr{X}{i\delta}$.
Therefore,
%
\begin{align*}
& \reach{H}{(i+1)\delta}{X_0}
= \reach{H}{\delta}{\reach{H}{i\delta}{X_0}} \subseteq \reach{H}{\delta}{\tr{X}{i\delta}}
\subseteq \ztset{\flow{H}{\delta}{K}{\epsilon}{\tr{X}{i\delta}}}\\
& = \ztset{\tr{X}{i\delta}}.\%~\text{by Step~\ref{step:1} in Algorithm~\ref{alg:main}}\\
%
& \forall t\in(i\delta,(i+1)\delta)~\reach{H}{t}{X_0}
= \reach{H}{t-i\delta}{\reach{H}{i\delta}{X_0}} \subseteq \reach{H}{[0,\delta]}{\tr{X}{i\delta}}
\subseteq \ztset{\ivflow{H}{\delta}{K}{\epsilon}{\tr{X}{i\delta}}}\\
& = \ztset{\tr{X}{t}}. \%~\text{by Step~\ref{step:2} Algorithm~\ref{alg:main}}
\end{align*}
%
This proves the claim made above.

Then it follows by induction that the theorem is true if
$X_0\subseteq \tr{X}{0}$.  We have $\tr{X}{0} = \iouopt{\eta}{X_0}$,
which is constructed by dividing $X_0$ by different optimized division
vectors and intersecting the unions and results in a sound
overapproximation of $X_0$.  Therefore, the theorem is true.
\end{proof}
%
